|

### 2021-05-11 01-Chp-Background.Rmd
End of day: -2767
End of day: -3892

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2:
    reference_docx: templates/word-styles-reference-01.docx
    number_sections: false 
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
documentclass: book
---

@@

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2:
    reference_docx: templates/word-styles-reference-01.docx
    number_sections: false 
  bookdown::html_document2: default
documentclass: book
---

@@

<!--- May need small bit here on converting from one measurement to the other i.e.
mg/dL to mmol/L--->
